Modular Model-Checking Implementations of a Byzantine Fault-Tolerant Protocol

### 2016-12-07 doc/om-paper/paper.tex

But the relationship between many of the state variables often has an intuitive structure, one familiar to the designer, that can be characterized by a state machine imposed over it. The state machine describes discrete modes or configurations. Each mode captures a relation on a subset of the state variables, as well as the set of possible modes that follow.

This idea is an implementation of abstract state machines (ASMs). ASMs are a generalization of finite state machines originally developed by Gurevich to generalize state machines to operate over arbitrary data structures~\cite{}. In our context, we require only a restricted form of ASMs known as a \emph{sequential small-step ASM}:

\begin{definition}[Abstract state machine (ASM)]

\lee{Ben will redo. I'd just remove the Gurevich reference}
\ben{I still need to do this!}

>>>>

But the relationship between many of the state variables often has an intuitive structure, one familiar to the designer, that can be characterized by an auxiliary state machine imposed over it. The state space of this auxiliary machine comprises discrete modes or configurations of the real system. Each mode captures a relation on a subset of the state variables, as well as the set of possible modes that follow.

\cite{timed-systems}
\cite{Rushby00:CAV}

% This idea is an implementation of abstract state machines (ASMs). ASMs are a generalization of finite state machines originally developed by Gurevich to generalize state machines to operate over arbitrary data structures~\cite{asm}. In our modeling framework we take the ASM idea and turn it into both and auxiliary state machine and an observer of the real system as follows.

% In our context, we require only a restricted form of ASMs known as a \emph{sequential small-step ASM}:

\begin{definition}[Abstract state machine observer (ASMO)]
